---
title: "Hippocampus and Aerobic Exercise Review"
author: "Guilherme Moraes Balbim"
date: "11/30/2022"
output: 
  pdf_document: 
    toc: yes
    number_sections: yes
    toc_depth: 5
  word_document: 
    toc: yes
    toc_depth: 5
geometry: "left = 1cm, right = 1cm, top = 1cm, bottom = 2.5cm"
header-includes:
- \usepackage{caption}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
editor_options: 
  chunk_output_type: console
---

\newpage

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  fig.height = 7, fig.width = 9, fig.align = "center")
```

\small

# Loading packages

```{r, message=FALSE}

if (!require("pacman")) install.packages("pacman")
pacman::p_load(readxl, janitor, plyr, robumeta, dplyr, metafor, clubSandwich, ggplot2, psych, devtools, tidyverse, stringr, knitr, tableone, tinytex)

```

# Loading the data
```{r, message=FALSE}

ex_hpc_data <- read_csv("Hippocampus_MetaAnalysis_Agreement_BDNF_20221115.csv", 
                         show_col_types = FALSE,
                         name_repair = make_clean_names,
                        col_select = c(1:3, 5:9, 11:32))

```

# Prepping the data
```{r, message=FALSE}

# Combine author with year, and study_year with contrast
ex_hpc_data_prep <-  ex_hpc_data %>%
  dplyr::rename(outcome_type = outcome_1) %>% 
  unite("study_year", author:year) %>% 
  unite("study_year_int_dpt", study_year, contrast, sep = "_", remove = FALSE) %>%
  mutate(total_n = m_n + f_n,
         pct_f = round((f_n*100/total_n), 2)) %>%
  relocate(c(total_n, pct_f), .after = f_n) %>% 
  dplyr::select(-c(contrast))

table(ex_hpc_data_prep$study_year)

```

# Calculating Hedge's g
```{r, message=FALSE}

ex_hpc_data_g <- ex_hpc_data_prep %>% 
  mutate(var_d = (((pre_exp_n + pre_con_n) / (pre_exp_n * pre_con_n)) + ((smd^2) / (2*(pre_exp_n + pre_con_n)))),
         j = (1 - (3/(4 * (pre_exp_n + pre_con_n -2) - 1))),
         hedges_g = smd*j,
         var_g = j^2*var_d,
         se_g = var_g/(pre_exp_n + pre_con_n))

describeBy(ex_hpc_data_g$hedges_g, ex_hpc_data_g$outcome_type)

```

# Subsetting by outcome type and transforming to wide
```{r, message=FALSE}

# Subsetting
ex_hpc_data_g_hpc <- ex_hpc_data_g %>% 
  filter(outcome_type == "Hippocampus")

ex_hpc_data_g_memory <- ex_hpc_data_g %>% 
  filter(outcome_type == "Memory")

ex_hpc_data_g_crf <- ex_hpc_data_g %>% 
  filter(outcome_type == "CRF")

ex_hpc_data_g_bdnf <- ex_hpc_data_g %>% 
  filter(outcome_type == "BDNF")

# Transforming to wide
## Hippocampus
ex_hpc_data_g_hpc_wide_1 <- ex_hpc_data_g_hpc %>%
  group_by(study_year_int_dpt) %>% 
  mutate(time = seq_along(study_year)) %>% 
  ungroup()

ex_hpc_data_g_hpc_wide <- ex_hpc_data_g_hpc_wide_1 %>% 
  pivot_wider(id_cols = study_year_int_dpt, names_from = time, values_from = c(hedges_g, var_g))

### Rowmeans
ex_hpc_data_g_hpc_wide_rmeans <- ex_hpc_data_g_hpc_wide %>% 
  mutate(hpc_g = rowMeans(ex_hpc_data_g_hpc_wide[c(2:4)],na.rm = TRUE), 
         hpc_var_g = rowMeans(ex_hpc_data_g_hpc_wide[c(5:7)],na.rm = TRUE))
         

hpc_g_var <- ex_hpc_data_g_hpc_wide_rmeans %>% 
  dplyr::select(1,8,9)

## Memory
ex_hpc_data_g_memory_wide_1 <- ex_hpc_data_g_memory %>%
  group_by(study_year_int_dpt) %>% 
  mutate(time = seq_along(study_year)) %>% 
  ungroup()

ex_hpc_data_g_memory_wide <- ex_hpc_data_g_memory_wide_1 %>% 
  pivot_wider(id_cols = study_year_int_dpt, names_from = time, values_from = c(hedges_g, var_g))

### Rowmeans
ex_hpc_data_g_memory_wide_rmeans <- ex_hpc_data_g_memory_wide %>% 
  mutate(memory_g = rowMeans(ex_hpc_data_g_memory_wide[c(2:7)],na.rm = TRUE), 
         memory_var_g = rowMeans(ex_hpc_data_g_memory_wide[c(8:13)],na.rm = TRUE))

memory_g_var <- ex_hpc_data_g_memory_wide_rmeans %>% 
  dplyr::select(1,14,15)

## CRF
ex_hpc_data_g_crf_wide_1 <- ex_hpc_data_g_crf %>%
  group_by(study_year_int_dpt) %>% 
  mutate(time = seq_along(study_year)) %>% 
  ungroup()

ex_hpc_data_g_crf_wide <- ex_hpc_data_g_crf_wide_1 %>% 
  pivot_wider(id_cols = study_year_int_dpt, names_from = time, values_from = c(hedges_g, var_g))

### Rowmeans
ex_hpc_data_g_crf_wide_rmeans <- ex_hpc_data_g_crf_wide %>% 
  mutate(crf_g = rowMeans(ex_hpc_data_g_crf_wide[2],na.rm = TRUE),
         crf_var_g = rowMeans(ex_hpc_data_g_crf_wide[3],na.rm = TRUE))

crf_g_var <- ex_hpc_data_g_crf_wide_rmeans %>% 
  dplyr::select(1,4,5)

## BDNF
ex_hpc_data_g_bdnf_wide_1 <- ex_hpc_data_g_bdnf %>%
  group_by(study_year_int_dpt) %>% 
  mutate(time = seq_along(study_year)) %>% 
  ungroup()

ex_hpc_data_g_bdnf_wide <- ex_hpc_data_g_bdnf_wide_1 %>% 
  pivot_wider(id_cols = study_year_int_dpt, names_from = time, values_from = c(hedges_g, var_g))

### Rowmeans
ex_hpc_data_g_bdnf_wide_rmeans <- ex_hpc_data_g_bdnf_wide %>% 
  mutate(bdnf_g = rowMeans(ex_hpc_data_g_bdnf_wide[2],na.rm = TRUE),
         bdnf_var_g = rowMeans(ex_hpc_data_g_bdnf_wide[3],na.rm = TRUE))

bdnf_g_var <- ex_hpc_data_g_bdnf_wide_rmeans %>% 
  dplyr::select(1,4,5)

# Join the datasets
df_list <- list(ex_hpc_data_g, hpc_g_var, memory_g_var, crf_g_var, bdnf_g_var)

ex_hpc_data_final <- df_list %>% 
  reduce(full_join, by = "study_year_int_dpt")

```

# Meta-analysis
## Hippocampus
```{r, message=FALSE}

ex_hpc_data_hpc <- ex_hpc_data_final %>% 
  filter(outcome_type == "Hippocampus") %>% 
  filter(!str_detect(study_year_int_dpt, "Year_5")) %>% 
  filter(!str_detect(study_year_int_dpt, "Year_3")) 

hippocampus.g <- robu(hedges_g~1,var=var_g,studynum=study_year_int_dpt,ex_hpc_data_hpc) # Clustered at level of overall study
print(hippocampus.g)
sensitivity(hippocampus.g)

# Extract 95% CI
hippocampus.g[["data"]][["ci.u"]] <- hippocampus.g[["data.full"]][["effect.size"]]+(1.96*sqrt(hippocampus.g[["data.full"]][["var.eff.size"]]))
hippocampus.g[["data"]][["ci.l"]] <- hippocampus.g[["data.full"]][["effect.size"]]-(1.96*sqrt(hippocampus.g[["data.full"]][["var.eff.size"]]))
hippocampus.g[["data"]][["ci"]] <- paste("[",format(round(hippocampus.g[["data"]][["ci.l"]], 3), nsmall = 3), "; ", 
                                         format(round(hippocampus.g[["data"]][["ci.u"]], 3), nsmall = 3), "]", sep = "")

hippocampus.g[["data"]][["study_year_int_dpt"]] <- hippocampus.g[["data"]][["study_year_int_dpt"]] %>% 
  str_replace_all("_", " ") %>% 
  str_replace_all("AT CON Baseline", "") %>% 
  str_replace_all(" CON Baseline Year 1", "") %>% 
  str_replace_all("  3mo", "") %>% 
  str_replace_all("  12mo", "") %>%
  str_replace_all("  6mo", "")  %>% 
  str_replace_all(c("2022" = "(2022)", "2020" = "(2020)", "2011" = "(2011)", "2017" = "(2017)", "2015" = "(2015)", "2014" = "(2014)"))

hippocampus.g[["data"]][["measure"]] <- hippocampus.g[["data"]][["measure"]] %>% 
  str_replace_all("_", ", ")

forest.robu(hippocampus.g,es.lab="measure",study.lab="study_year_int_dpt",
                         "Hedges' g" = effect.size,
                         "95% CI" = ci,
                         "Weight" = r.weights)

```

## Memory
```{r, message=FALSE}

ex_hpc_data_memory <- ex_hpc_data_final %>% 
  filter(outcome_type == "Memory") %>% 
  filter(!str_detect(study_year_int_dpt, "Year_5")) %>% 
  filter(!str_detect(study_year_int_dpt, "Year_3"))

memory.g <- robu(hedges_g~1,var=var_g,studynum=study_year_int_dpt,ex_hpc_data_memory) # Clustered at level of overall study
print(memory.g)
sensitivity(memory.g)

# Extract 95% CI
memory.g[["data"]][["ci.u"]] <- memory.g[["data.full"]][["effect.size"]]+(1.96*sqrt(memory.g[["data.full"]][["var.eff.size"]]))
memory.g[["data"]][["ci.l"]] <- memory.g[["data.full"]][["effect.size"]]-(1.96*sqrt(memory.g[["data.full"]][["var.eff.size"]]))
memory.g[["data"]][["ci"]] <- paste("[",format(round(memory.g[["data"]][["ci.l"]], 3), nsmall = 3), "; ", 
                                         format(round(memory.g[["data"]][["ci.u"]], 3), nsmall = 3), "]", sep = "")

memory.g[["data"]][["study_year_int_dpt"]] <- memory.g[["data"]][["study_year_int_dpt"]] %>% 
  str_replace_all("_", " ") %>% 
  str_replace_all("AT CON Baseline", "") %>% 
  str_replace_all(" CON Baseline Year 1", "") %>% 
  str_replace_all("  3mo", "") %>% 
  str_replace_all("  12mo", "") %>%
  str_replace_all("  6mo", "")  %>% 
  str_replace_all(c("2022" = "(2022)", "2020" = "(2020)", "2011" = "(2011)", "2017" = "(2017)", "2015" = "(2015)", "2014" = "(2014)"))

memory.g[["data"]][["measure"]] <- memory.g[["data"]][["measure"]] %>% 
  str_replace_all("_", " ")

forest.plot_memory<-forest.robu(memory.g,es.lab="measure",study.lab="study_year_int_dpt",
                         "Hedges' g" = effect.size,
                         "95% CI" = ci,
                         "Weight" = r.weights)

```

## CRF
```{r, message=FALSE}

ex_hpc_data_crf <- ex_hpc_data_final %>% 
  filter(outcome_type == "CRF") %>% 
  filter(!str_detect(study_year_int_dpt, "Year_5")) %>% 
  filter(!str_detect(study_year_int_dpt, "Year_3"))

crf.g <- robu(hedges_g~1,var=var_g,studynum=study_year_int_dpt,ex_hpc_data_crf) # Clustered at level of overall study
print(crf.g)
sensitivity(crf.g)

# Extract 95% CI
crf.g[["data"]][["ci.u"]] <- crf.g[["data.full"]][["effect.size"]]+(1.96*sqrt(crf.g[["data.full"]][["var.eff.size"]]))
crf.g[["data"]][["ci.l"]] <- crf.g[["data.full"]][["effect.size"]]-(1.96*sqrt(crf.g[["data.full"]][["var.eff.size"]]))
crf.g[["data"]][["ci"]] <- paste("[",format(round(crf.g[["data"]][["ci.l"]], 3), nsmall = 3), "; ", 
                                         format(round(crf.g[["data"]][["ci.u"]], 3), nsmall = 3), "]", sep = "")

crf.g[["data"]][["study_year_int_dpt"]] <- crf.g[["data"]][["study_year_int_dpt"]] %>% 
  str_replace_all("_", " ") %>% 
  str_replace_all("AT CON Baseline", "") %>% 
  str_replace_all(" CON Baseline Year 1", "") %>% 
  str_replace_all("  3mo", "") %>% 
  str_replace_all("  12mo", "") %>%
  str_replace_all("  6mo", "")  %>% 
  str_replace_all(c("2022" = "(2022)", "2020" = "(2020)", "2011" = "(2011)", "2017" = "(2017)", "2015" = "(2015)", "2014" = "(2014)"))

crf.g[["data"]][["measure"]] <- crf.g[["data"]][["measure"]] %>% 
  str_replace_all("_", " ")

forest.plot_crf<-forest.robu(crf.g,es.lab="measure",study.lab="study_year_int_dpt",
                         "Hedges' g" = effect.size,
                         "95% CI" = ci,
                         "Weight" = r.weights)

```

## BDNF (exploratory unpublished analysis)
```{r, message=FALSE}

ex_hpc_data_bdnf <- ex_hpc_data_final %>% 
  filter(outcome_type == "BDNF") %>% 
  filter(!str_detect(study_year_int_dpt, "Year_5")) %>% 
  filter(!str_detect(study_year_int_dpt, "Year_3"))

bdnf.g <- robu(hedges_g~1,var=var_g,studynum=study_year_int_dpt,ex_hpc_data_bdnf) # Clustered at level of overall study
print(bdnf.g)
sensitivity(bdnf.g)

# Extract 95% CI
bdnf.g[["data"]][["ci.u"]] <- bdnf.g[["data.full"]][["effect.size"]]+(1.96*sqrt(bdnf.g[["data.full"]][["var.eff.size"]]))
bdnf.g[["data"]][["ci.l"]] <- bdnf.g[["data.full"]][["effect.size"]]-(1.96*sqrt(bdnf.g[["data.full"]][["var.eff.size"]]))
bdnf.g[["data"]][["ci"]] <- paste("[",format(round(bdnf.g[["data"]][["ci.l"]], 3), nsmall = 3), "; ", 
                                         format(round(bdnf.g[["data"]][["ci.u"]], 3), nsmall = 3), "]", sep = "")

bdnf.g[["data"]][["study_year_int_dpt"]] <- bdnf.g[["data"]][["study_year_int_dpt"]] %>% 
  str_replace_all("_", " ") %>% 
  str_replace_all("AT CON Baseline", "") %>% 
  str_replace_all(" CON Baseline Year 1", "") %>% 
  str_replace_all("  3mo", "") %>% 
  str_replace_all("  12mo", "") %>%
  str_replace_all("  6mo", "")  %>% 
  str_replace_all(c("2022" = "(2022)", "2020" = "(2020)", "2011" = "(2011)", "2017" = "(2017)", "2015" = "(2015)", "2014" = "(2014)"))

bdnf.g[["data"]][["measure"]] <- bdnf.g[["data"]][["measure"]] %>% 
  str_replace_all("_", " ")

forest.plot_bdnf<-forest.robu(bdnf.g,es.lab="measure",study.lab="study_year_int_dpt",
                         "Hedges' g" = effect.size,
                         "95% CI" = ci,
                         "Weight" = r.weights)

```

# Leave-one-out analysis
## Hippocampus
```{r, message=FALSE}

hippocampus.g<-robu(hedges_g~1,var=var_g,studynum=study_year_int_dpt,ex_hpc_data_hpc)
print(hippocampus.g)

leave.one.out <- function(rownum){
  
  # subset dataframe
  vec <- rep(TRUE, nrow(ex_hpc_data_hpc))
  vec[rownum] <- FALSE
  inf <- subset(ex_hpc_data_hpc, vec)
  
  # fit reference model
  rve.model.ref <- robu(hedges_g~1,var=var_g,studynum=study_year_int_dpt,ex_hpc_data_hpc)
  
  # fit adjusted model
  rve.model <- robu(hedges_g~1,var=var_g,studynum=study_year_int_dpt, data = inf)
  
  # return results
  results.vec <- c(g.study = round(ex_hpc_data_hpc$hedges_g[rownum], 3),
                   g.adj = round(rve.model$reg_table$b.r, 3),
                   se.g.adj = round(rve.model$reg_table$SE, 3),
                   p.adj = round(rve.model$reg_table$prob, 5),
                   diff.g = round(rve.model$reg_table$b.r - rve.model.ref$reg_table$b.r, 3),
                   diff.se.g = round(rve.model$reg_table$SE - rve.model.ref$reg_table$SE, 3),
                   diff.p = round(rve.model$reg_table$prob - rve.model.ref$reg_table$prob, 5),
                   diff.isq = round(rve.model$mod_info$I.2 - rve.model.ref$mod_info$I.2, 3))
  return(results.vec)
}


inf.hpc <- sapply(1:nrow(ex_hpc_data_hpc), leave.one.out)
inf.hpc <- data.frame(t(inf.hpc))
inf.hpc <- data.frame(label = paste(ex_hpc_data_hpc$study_year_int_dpt, ex_hpc_data_hpc$outcome_type, sep = " / "),
                      inf.hpc)
inf.hpc$z.g.study <- round(scale(inf.hpc$g.study), 2)
inf.hpc$g.min.sumeff.div.sdg <- round((ex_hpc_data_hpc$hedges_g - hippocampus.g$reg_table$b.r) / sd(ex_hpc_data_hpc$hedges_g), 2)

View(inf.hpc)

```

## Memory
```{r, message=FALSE}

memory.g<-robu(hedges_g~1,var=var_g,studynum=study_year_int_dpt,ex_hpc_data_memory)
print(memory.g)

leave.one.out <- function(rownum){
  
  # subset dataframe
  vec <- rep(TRUE, nrow(ex_hpc_data_memory))
  vec[rownum] <- FALSE
  inf <- subset(ex_hpc_data_memory, vec)
  
  # fit reference model
  rve.model.ref <- robu(hedges_g~1,var=var_g,studynum=study_year_int_dpt,ex_hpc_data_memory)
  
  # fit adjusted model
  rve.model <- robu(hedges_g~1,var=var_g,studynum=study_year_int_dpt, data = inf)
  
  # return results
  results.vec <- c(g.study = round(ex_hpc_data_memory$hedges_g[rownum], 3),
                   g.adj = round(rve.model$reg_table$b.r, 3),
                   se.g.adj = round(rve.model$reg_table$SE, 3),
                   p.adj = round(rve.model$reg_table$prob, 5),
                   diff.g = round(rve.model$reg_table$b.r - rve.model.ref$reg_table$b.r, 3),
                   diff.se.g = round(rve.model$reg_table$SE - rve.model.ref$reg_table$SE, 3),
                   diff.p = round(rve.model$reg_table$prob - rve.model.ref$reg_table$prob, 5),
                   diff.isq = round(rve.model$mod_info$I.2 - rve.model.ref$mod_info$I.2, 3))
  return(results.vec)
}


inf.memory <- sapply(1:nrow(ex_hpc_data_memory), leave.one.out)
inf.memory <- data.frame(t(inf.memory))
inf.memory <- data.frame(label = paste(ex_hpc_data_memory$study_year_int_dpt, ex_hpc_data_memory$outcome_type, sep = " / "),
                      inf.memory)
inf.memory$z.g.study <- round(scale(inf.memory$g.study), 2)
inf.memory$g.min.sumeff.div.sdg <- round((ex_hpc_data_memory$hedges_g - hippocampus.g$reg_table$b.r) / sd(ex_hpc_data_memory$hedges_g), 2)

View(inf.memory)

```

## CRF
```{r, message=FALSE}

crf.g<-robu(hedges_g~1,var=var_g,studynum=study_year_int_dpt,ex_hpc_data_crf)
print(crf.g)

leave.one.out <- function(rownum){
  
  # subset dataframe
  vec <- rep(TRUE, nrow(ex_hpc_data_crf))
  vec[rownum] <- FALSE
  inf <- subset(ex_hpc_data_crf, vec)
  
  # fit reference model
  rve.model.ref <- robu(hedges_g~1,var=var_g,studynum=study_year_int_dpt,ex_hpc_data_crf)
  
  # fit adjusted model
  rve.model <- robu(hedges_g~1,var=var_g,studynum=study_year_int_dpt, data = inf)
  
  # return results
  results.vec <- c(g.study = round(ex_hpc_data_crf$hedges_g[rownum], 3),
                   g.adj = round(rve.model$reg_table$b.r, 3),
                   se.g.adj = round(rve.model$reg_table$SE, 3),
                   p.adj = round(rve.model$reg_table$prob, 5),
                   diff.g = round(rve.model$reg_table$b.r - rve.model.ref$reg_table$b.r, 3),
                   diff.se.g = round(rve.model$reg_table$SE - rve.model.ref$reg_table$SE, 3),
                   diff.p = round(rve.model$reg_table$prob - rve.model.ref$reg_table$prob, 5),
                   diff.isq = round(rve.model$mod_info$I.2 - rve.model.ref$mod_info$I.2, 3))
  return(results.vec)
}


inf.crf <- sapply(1:nrow(ex_hpc_data_crf), leave.one.out)
inf.crf <- data.frame(t(inf.crf))
inf.crf <- data.frame(label = paste(ex_hpc_data_crf$study_year_int_dpt, ex_hpc_data_crf$outcome_type, sep = " / "),
                      inf.crf)
inf.crf$z.g.study <- round(scale(inf.crf$g.study), 2)
inf.crf$g.min.sumeff.div.sdg <- round((ex_hpc_data_crf$hedges_g - hippocampus.g$reg_table$b.r) / sd(ex_hpc_data_crf$hedges_g), 2)

View(inf.crf)

```

# Meta-regressions
## CRF ES predicting HPC ES
```{r, message=FALSE}

df_list_2 <- list(hpc_g_var, memory_g_var, crf_g_var, bdnf_g_var)

hpc_memory_crf_bdnf_g_var <- df_list_2 %>% 
  reduce(full_join, by = "study_year_int_dpt")

# Cleaning study_year_int_dpt 
hpc_memory_crf_bdnf_g_var <- hpc_memory_crf_bdnf_g_var %>% 
  filter(!str_detect(study_year_int_dpt, "Year_5")) %>% 
  filter(!str_detect(study_year_int_dpt, "Year_3")) %>% 
  mutate(study_year_int_dpt = str_replace_all(study_year_int_dpt,"_", " "),
         study_year_int_dpt = str_replace_all(study_year_int_dpt," CON", ","),
         study_year_int_dpt = str_replace(study_year_int_dpt, "2", "(2"),
         study_year_int_dpt = str_replace(study_year_int_dpt, "22", "22),"),
         study_year_int_dpt = str_replace(study_year_int_dpt, "11", "11),"),
         study_year_int_dpt = str_replace(study_year_int_dpt, "17", "17),"),
         study_year_int_dpt = str_replace(study_year_int_dpt, "15", "15),"),
         study_year_int_dpt = str_replace(study_year_int_dpt, "14", "14),"),
         study_year_int_dpt = str_replace_all(study_year_int_dpt,"Baseline", "Baseline X"),
         study_year_int_dpt = str_replace_all(study_year_int_dpt,"mo", "-month"))
  

crf.hpc.es <- rma(yi=hpc_g, vi=hpc_var_g, mods = ~crf_g+crf_var_g, data = hpc_memory_crf_bdnf_g_var, slab = study_year_int_dpt, method = "DL")
crf.hpc.es

crf_v_hpc <- ggplot(aes(x = crf_g, y = hpc_g, size = (1/hpc_var_g)), data = hpc_memory_crf_bdnf_g_var) + geom_point(aes(colour = study_year_int_dpt)) +
  geom_abline(aes(intercept = crf.hpc.es$b[1], slope = crf.hpc.es$b[2]), size = 1) + 
  ylab("Hippocampal volume effect size") + guides(size="none") + scale_colour_discrete("Study, intervention type, and time-points") +
  ylim(-0.25, 0.5) +
  xlab("CRF effect size") +
  xlim(-0.2, 1.5) +
  theme_bw(base_size = 12)

crf_v_hpc

ggsave(crf_v_hpc, height= 10, width= 14, file="crf_predict_hpc_20220916.jpeg", dpi = 300)
  

```

## CRF ES predicting Memory ES
```{r, message=FALSE}

crf.memory.es <- rma(yi=memory_g, vi=memory_var_g, mods = ~crf_g+crf_var_g, data = hpc_memory_crf_bdnf_g_var, slab = study_year_int_dpt, method = "DL")
crf.memory.es

crf_v_memory <- ggplot(aes(x = crf_g, y = memory_g, size = (1/memory_var_g)), data = hpc_memory_crf_bdnf_g_var) + geom_point(aes(colour = study_year_int_dpt)) +
  geom_abline(aes(intercept = crf.memory.es$b[1], slope = crf.memory.es$b[2]), size = 1) + 
  ylab("Memory effect size") + guides(size="none") + scale_colour_discrete("Study, intervention type, and time-points") +
  ylim(-0.25, 0.5) +
  xlab("CRF effect size") +
  xlim(-0.2, 1.5) +
  theme_bw(base_size = 12)

crf_v_memory

ggsave(crf_v_memory, height= 10, width= 14, file="crf_predict_memory.jpeg", dpi = 300)

```

## CRF ES predicting BDNF ES (exploratory unpublished analysis)
```{r, message=FALSE}

# crf.bdnf.es <- rma(yi=bdnf_g, vi=bdnf_var_g, mods = ~crf_g+crf_var_g, data = hpc_memory_crf_bdnf_g_var, slab = study_year_int_dpt, method = "DL")
# crf.bdnf.es
# Number of parameters to be estimated is larger than the number of observations.

```

## HPC ES predicting Memory ES
```{r, message=FALSE}

hpc.memory.es <- rma(yi=memory_g, vi=memory_var_g, mods = ~hpc_g+hpc_var_g, data = hpc_memory_crf_bdnf_g_var, slab = study_year_int_dpt, method = "DL")
hpc.memory.es

hpc_v_memory <- ggplot(aes(x = hpc_g, y = memory_g, size = (1/memory_var_g)), data = hpc_memory_crf_bdnf_g_var) + geom_point(aes(colour = study_year_int_dpt)) +
  geom_abline(aes(intercept = hpc.memory.es$b[1], slope = hpc.memory.es$b[2]), size = 1) + 
  ylab("Memory effect size") + guides(size="none") + scale_colour_discrete("Study, intervention type, and time-points") +
  ylim(-0.5, 0.5) +
  xlab("Hippocampal volume effect size") +
  xlim(-0.5, 0.5) +
  theme_bw(base_size = 12)

hpc_v_memory

ggsave(hpc_v_memory, height= 10, width= 14, file="hpc_predict_memory.jpeg", dpi = 300)

```

## BDNF ES predicting HPC ES (exploratory unpublished analysis)
```{r, message=FALSE}

bdnf.hpc.es <- rma(yi=hpc_g, vi=hpc_var_g, mods = ~bdnf_g+bdnf_var_g, data = hpc_memory_crf_bdnf_g_var, slab = study_year_int_dpt, method = "DL")
bdnf.hpc.es
# DF is too low.

```

# Small study effect and publication bias
```{r, message=FALSE}

# Egger's regression test for dependent effect sizes
eggers_hpc <- robu(hedges_g~se_g, var.eff.size = var_g, studynum = study_year_int_dpt, ex_hpc_data_hpc)
eggers_hpc

eggers_memory <- robu(hedges_g~se_g, var.eff.size = var_g, studynum = study_year_int_dpt, ex_hpc_data_memory)
eggers_memory

eggers_crf <- robu(hedges_g~se_g, var.eff.size = var_g, studynum = study_year_int_dpt, ex_hpc_data_crf)
eggers_crf

# Funnel plots
funnel_hpc <- rma.mv(yi = hedges_g, V = var_g, random = ~factor(study_year_int_dpt)|study_year, data = ex_hpc_data_hpc, slab = study_year_int_dpt)
funnel(funnel_hpc, xlab = "Hedges' g for hippocampal volume")

funnel_memory <- rma.mv(yi = hedges_g, V = var_g, random = ~factor(study_year_int_dpt)|study_year, data = ex_hpc_data_memory, slab = study_year_int_dpt)
funnel(funnel_memory, xlab = "Hedges' g for memory")

funnel_crf <- rma.mv(yi = hedges_g, V = var_g, random = ~factor(study_year_int_dpt)|study_year, data = ex_hpc_data_crf, slab = study_year_int_dpt)
funnel(funnel_crf, xlab = "Hedges' g for CRF")

```

# PEESE
```{r, message=FALSE}

ex_hpc_data_hpc <- ex_hpc_data_hpc %>% 
  mutate(sqrt_se_g = se_g^2)

ex_hpc_data_memory <- ex_hpc_data_memory %>% 
  mutate(sqrt_se_g = se_g^2)

ex_hpc_data_crf <- ex_hpc_data_crf %>% 
  mutate(sqrt_se_g = se_g^2)

peese_rve_hpc <- robu(hedges_g~sqrt_se_g, var.eff.size = var_g, studynum = study_year_int_dpt, ex_hpc_data_hpc)
print(peese_rve_hpc)

peese_rve_memory <- robu(hedges_g~sqrt_se_g, var.eff.size = var_g, studynum = study_year_int_dpt, ex_hpc_data_memory)
print(peese_rve_memory)

peese_rve_crf <- robu(hedges_g~sqrt_se_g, var.eff.size = var_g, studynum = study_year_int_dpt, ex_hpc_data_crf)
print(peese_rve_crf)

```

# Descriptives
```{r, message=FALSE}

kable(digits = 2, print(printToggle = FALSE, CreateTableOne(data = ex_hpc_data_g, 
                                                c("age",
                                                  "total_n",
                                                  "pct_f",
                                                  "duration_mo"), includeNA = TRUE, addOverall = TRUE)))

```